\section{Schedule}

%A schedule, specifying concretely what you intend to have accomplished by each
%of the two milestones below as well as for the final report/presentation. It is
%perfectly acceptable if the final deliverable is not a completion of the
%project---which, if successful, some members of the group may wish to continue
%after the term ends---but it does need to be something that can be clearly
%demonstrated/evaluated/graded.

\subsection{Feb. 19}
\begin{enumerate}
\item All hardware in-hand, cataloged, and tested. We will have documented all the listed features and performance of all devices we will be testing.
\item A testing suite, with associated metrics and benchmarking tools.
\item Preliminary results from running the testing tools on our 802.11ac and 802.11 g/n networks in isolation (no notable RF interference)
\end{enumerate}

\subsection{Mar. 5}
\begin{enumerate}
\item Testing results from interference of 802.11ac and g/n networks in both RF and spatial interference
\item Testing results for beamforming/spatial stream effects on interference
\end{enumerate}
This is basically all of our data collection near
complete. Hopefully. There is enough time after this that if some
parts slip we can continue tests.

\subsection{Final}
Full data on interference between 802.11ac and 802.11b/g/n networks. This will include:
\begin{enumerate}
\item Baseline data of what our hardware is capable of in isolation
\item 802.11ac performance degredation in varying levels of 802.11b/g/n traffic
\item 802.11b/g/n performance degredation in the presence of 802.11ac
\item Above two, but with 802.11ac using spatial streams/beamforming
\item Analysis of our results, based on both previous works (see
  related work) and on what level of introspection we are able to
  obtain during the project.
\end{enumerate}

I use 802.11b/g/n in this, since we are certain to use n, but are
unsure if we will have time to do any meaningful testing comparing all
802.11 consumer technologies.
