\section{Conclude}
Wireless measurement is difficult. Changing environmental factors and
lack of device introspection make drawing serious conclusions nearly
impossible with the current state of 802.11ac consumer products.

We have shown, however, that 80MHz channel widths perform
approximately as expected, increasing received signal strength both
indoors and outdoors, and increasing the maximum connection distance.
Unfortunately, most devices experience a net throughput reduction with
80MHz in the longest distance scenarios due to a combination of MCS
choice and a reduction (in the case of the Macbook and the Intel 7260)
to a single spatial stream under 80MHz.

We have learned that for future iterations of this project we need to increase the data set size.
This includes collecting frame captures at both end points and perferably on the AP as well. We also
have learned that more research needs to go into our equipment selection to better understand
the networking stack on each piece of equipment. We also need to select equipment that provides a symetrical set of data, mainly all wireless equipment should be able to capture at full speed and provide full wiretap header information. Another factor to consider when we choose devices is the available storage capacity. We ran into collection issues on the Surface with hard drive storage space which limited our collection size.

We also learned that a considerable amount of time must be set aside for analyzing the data in order to extract information from the data set and to find patterns and trends.
